The Globular Cluster System of the Auriga Simulations

### 2019-02-13 AurigaGCS.tex
Updates at ZoltaN

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
% TODO: last checked arXiv Jan 27, 2018
\end{itemize}

@@

TODO: (in discussion) Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.

>>>>

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
    log \sigma_0, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
    of GCs crossing the disk. New kinematical data does not support
    this claim for two particular OSC-GC pairs, and does seem consistent
    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
    that GC crossing the disk could also trigger formation of multiple OSCs!)
% TODO: last checked arXiv Feb 13, 2019
\end{itemize}

@@
